---
title: "intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(eee)
```

# 2 variables, error-in-variable regression
### Introduction

Let's create two variables, one of which we will designate as the y-axis variable and call y, and the other we shall designate as the x-axis variable and call x.

```{r create-data}
set.seed(0)
number_of_points <- 50
y <- rnorm(number_of_points)
x <- rnorm(number_of_points)
```

Of course, having generated the data ourselves, we can see y and x are not related to each other, but entirely random. Still, it is simple data we can use to explore this package's functions and error-in-variable models more broadly. The main thing that makes error-in-variable models different from standard ordinary least squares regression is that we can specify any value for $\lambda$ (lambda) that we want. Ordinary least squares regression is the special scenario where lambda is $\infty$ (infinity) because the y-variable has some error, but the x-variable has none. $\lambda$ is the quantity of the variance of the error in the y-variable divided by the variance of the error in the x-variable. So obviously when the x-variable has no error in it, then the positive variance of y's error divided by zero gives infinity. While my function does not actually accept $\infty$ as an input, we can see that putting a sufficiently large number, in this case 10^100 as the value for $\lambda$ gives an identical line to that traditionally obtained with OLS as we can see below:

```{r ols-comparison}
result_00 <- eee::two_variable_exact_CI(
  correlation = cor(x, y),
  sdOFy_divided_by_sdOFx = sd(y) / sd(x),
  square_root_of_lambda = sqrt(10^100),
  sample_size = number_of_points,
  print_citation_info = FALSE
)

result_00$slope_cartesian
```

is the same as:

```{r lm-comparison}
result_01 <- stats::lm(y ~ x)
summary(result_01)$coefficients["x", "Estimate"]
```
